### 2023-04-27 proofs/main.tex
WIP
finish completeness of lub; add initiality of lub
Add soundness of ≈
Add equivalence soundness and completeness proofs
Add equivalence and upgrade lemmas
Subtyping: soundness is done, completeness WIP

% P ≈ Q
\renewcommand{\ottdruleEOnePVarName}[0]{(Var$^+$)}
\renewcommand{\ottdruleEOneShiftDName}[0]{($\downarrow^{\eqEOne}$)}
\renewcommand{\ottdruleEOneExistsName}[0]{($\exists^{\eqEOne}$)}

@@

@@

Unification solution is represented by a list of unification solution entries.
Each entry restrict an unification variable in two possible ways: either stating
that it must be equivalent to a certain type ($[[Δ ⊢ pua :≈ iP]]$ or $[[Δ ⊢ nua :≈
iN]]$) or that it must be a (positive) supertype of a certain type ($[[Δ ⊢ pua :≥
iP]]$).

@@

Two matching entries can be merged in the following way:
\begin{definition} \hfill \\
\ottdefnSME\\
\end{definition}

@@

@@

@@

>>>>

% P ≈ Q
\renewcommand{\ottdruleEOnePVarName}[0]{(Var$^+$$^{\eqEOne}$)}
\renewcommand{\ottdruleEOneShiftDName}[0]{($\downarrow^{\eqEOne}$)}
\renewcommand{\ottdruleEOneExistsName}[0]{($\exists^{\eqEOne}$)}

@@

% G ⊢ N ≈1 M
\renewcommand{\ottdruleDOneNDefName}[0]{($\eqDOne^{-}$)}

% G ⊢ P ≈1 Q
\renewcommand{\ottdruleDOnePDefName}[0]{($\eqDOne^{+}$)}

% G ⊨ iP1 ∨ iP2 = iQ
\renewcommand{\ottdruleLUBVarName}[0]{(Var$^{\vee}$)}
\renewcommand{\ottdruleLUBShiftName}[0]{($\downarrow^{\vee}$)}
\renewcommand{\ottdruleLUBExistsName}[0]{($\exists^{\vee}$)}
\renewcommand{\ottdruleLUBUpgradeName}[0]{(Upg)}

% G ; Θ ⊨ uN ≤ iM ⫤ us
\renewcommand{\ottdruleANVarName}[0]{(Var$^-$$^{\subA}$)}
\renewcommand{\ottdruleAShiftUName}[0]{($\uparrow^{\subA}$)}
\renewcommand{\ottdruleAArrowName}[0]{($\rightarrow^{\subA}$)}
\renewcommand{\ottdruleAForallName}[0]{($\forall^{\subA}$)}

% G ; Θ ⊨ iP ≥ uQ ⫤ us
\renewcommand{\ottdruleAPVarName}[0]{(Var$^+$$^{\supA}$)}
\renewcommand{\ottdruleAShiftDName}[0]{($\downarrow^{\supA}$)}
\renewcommand{\ottdruleAExistsName}[0]{($\exists^{\supA}$)}
\renewcommand{\ottdruleAPUVarName}[0]{(UVar$^{\supA}$)}

@@

Unification solution is represented by a list of unification solution entries.
Each entry restricts an unification variable in two possible ways: either stating
that it must be equivalent to a certain type ($[[Δ ⊢ pua :≈ iP]]$ or $[[Δ ⊢ nua :≈
iN]]$) or that it must be a (positive) supertype of a certain type ($[[Δ ⊢ pua :≥
iP]]$).

@@

Two matching entries can be merged in the following way:
\begin{definition} \hfill \\
\ottdefnSME\\
\end{definition}
Notice that in case of equivalence, the assigned types
must be equal (i.e. alpha-equivalent) to be merged. This is because
the unification algorithm assumes that every type is normalized,
and hence, equivalence is alpha-equivalence 
(\cref{corollary:nf-complete-wrt-subt-equiv,corollary:nf-sound-wrt-subt-equiv}).

@@

\subsection{Declarative Subtyping}
\input{../_build/_gen/tex/decl-subtyping-lemmas.tex}

@@

\subsection{Upgrade}
\input{../_build/_gen/tex/upgrade-lemmas.tex}

@@

\subsection{Unification}
\input{../_build/_gen/tex/unification-lemmas.tex}\

\subsection{Anti-unification}
\input{../_build/_gen/tex/anti-unification-lemmas.tex}

\subsection{Solution Merge}
\input{../_build/_gen/tex/solution-merge-lemmas.tex}

\subsection{Subtyping Algorithm}
\input{../_build/_gen/tex/alg-subtyping-lemmas.tex}

### 2023-04-27 proofs/tex/equiv-lemmas.tex
Add equivalence and upgrade lemmas
Subtyping: soundness is done, completeness WIP

@@

>>>>

\begin{corollary}[Normalization is sound w.r.t. subtyping-induced equivalence] \label{corollary:nf-sound-wrt-subt-equiv}
  \hfill
  \begin{itemize}
    \item [$+$] if $[[Γ ⊢ iP]]$ then $[[Γ ⊢ iP ≈ nf(iP)]]$,
    \item [$-$] if $[[Γ ⊢ iN]]$ then $[[Γ ⊢ iN ≈ nf(iN)]]$.
  \end{itemize}
\end{corollary}
\begin{proof}
  Immediately from \cref{lemma:normalization-soundness,corollary:wf-nf,lemma:equiv-soundness}.
\end{proof}

@@

\begin{corollary}[Normalization is complete w.r.t. subtyping-induced equivalence]
  \label{corollary:nf-complete-wrt-subt-equiv}
  Assuming all the types below are well-formed in $[[Γ]]$:
  \begin{itemize}
    \item [$+$] if $[[Γ ⊢ iP ≈ iQ]]$ then $[[nf(iP) = nf(iQ)]]$,
    \item [$-$] if $[[Γ ⊢ iN ≈ iM]]$ then $[[nf(iN) = nf(iM)]]$.
  \end{itemize}
\end{corollary}  
\begin{proof}
  Immediately from \cref{lemma:equiv-completeness,lemma:normalization-completeness}.
\end{proof}
